Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-11-30 F_correction.tex
[paper] referee's suggestions done.

In the course of deriving the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state calculation in App.~\ref{app:lambda_12} (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable. However, free energy is not invariant under the conformal transformation since the boundaries partially break the conformal symmetry. In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term to get the correct exponent of the fidelity and Loschmidt echo.

@@

% staircase geometry correction
The annulus on the $\xi$ plane is called staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction. The traditional radial quantization however has radial direction to be the time. One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988} of the conformal transform
\begin{equation}
H_{\xi} = H_{w} - \frac{c}{24\pi} \beta .
\end{equation}
After the evolution for $2\pi$ (in the folding picture, the evolution is only $\pi$ but there are two bosons), the difference in the free energy is
\begin{equation}
F_{\xi} = F_{w} - \frac{c}{12} \beta .
\end{equation}
Gathering the two terms, we obtain the missing correction $\frac{c}{12} \beta$ between the slit and cylinder diagram, 
\begin{equation}
F_{z} = F_w + \frac{c}{12}\beta.
\end{equation}

>>>>

In the course of deriving the free energy subject to various boundary conditions, we use conformal transformation to convert the spacetime diagram with slits to a cylinder diagram, where the boundary state calculation in App.~\ref{app:lambda_12} (and ground state energy calculation in App.~\ref{app:gnd_dn_lambda}) is applicable. However, the free energy is not invariant under the conformal transformation since the boundaries partially break the conformal symmetry. In this Appendix, we point out two corrections -- one from the outer boundary regulator and the other from the inhomogeneous Schwartzian term to get the correct exponent of the fidelity and Loschmidt echo.

@@

% staircase geometry correction
The annulus on the $\xi$ plane is called the staircase geometry in Ref.~\onlinecite{cardy_finite-size_1988} due to its evolution in angular direction. The traditional radial quantization however has radial direction to be the time. One can show that the Hamiltonian of the staircase and rectangle has a shift due to the Schwartzian\cite{cardy_finite-size_1988} of the conformal transform
\begin{equation}
H_{\xi} = H_{w} - \frac{c}{24\pi} \beta .
\end{equation}
After the evolution for $2\pi$ (in the folding picture, the evolution is only $\pi$ but there are two bosons), the difference in the free energy is
\begin{equation}
F_{\xi} = F_{w} - \frac{c}{12} \beta .
\end{equation}
Gathering the two terms, we obtain the missing correction $\frac{c}{12} \beta$ between the slit and cylinder diagram, 
\begin{equation}
F_{z} = F_w + \frac{c}{12}\beta.
\end{equation}

### 2017-11-30 analy_eval.tex
[paper] referee's suggestions done.

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently use the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders. The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, so will not affect the fidelity and echo exponents.

@@

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

>>>>

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists a conformal map $\zeta(\xi)$ that maps the non-concentric circles to the two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, since the height of the cylinder is always $\pi$, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently use the leading order approximation to $\eta$ in the respective geometries and thus get the leading order term in the width of the cylinders. The slight deviation to the precise concentric geometry will only bring in $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to $\eta$ and the width parameter, so will not affect the fidelity and echo exponents.

@@

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and another part comes from the non-homogeneous term in the conformal transformation of the stress tensor from annulus to cylinder.

### 2017-11-30 compact_boson.tex
[paper] referee's suggestions done.

In this appendix, we address the issue of winding modes of compact bosons. In the main text, we have exclusively worked with the oscillator modes of free bosons. Here, we shall show that winding modes for compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order. Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.

@@

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.~\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
\begin{widetext}
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } ,
\end{aligned}
\end{equation}\end{widetext}
where $n,m$ are momentum and winding modes quantum numbers.

In Ref.~\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space. The boundary state we need here however lives on $x = 0$ -- a equal-space slice. We therefore compact the theory in time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as 
\begin{equation}
\label{eq:zzbar}
z = \exp( 2 \pi i \frac{t - x}{L}), \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L}).
\end{equation}
This corresponds to exchange the $x$ and $t$ in Ref.~\onlinecite{di_francesco_conformal_1997}.

>>>>

In this appendix, we address the issue of the winding modes of the compact bosons. In the main text, we have exclusively worked with the oscillator modes of the free bosons. Here, we shall show that winding modes for the compactified bosons will have no contribution to the fidelity or Loschmidt echo in the leading order. Therefore, our results are ready to be applied in the case where two compactified bosons of different radii are connected by a conformal interface\cite{PhysRevLett.118.136801}.

@@

\subsection{Mode Expansion of Compact Boson}
Suppose the boson is compactified as $\phi =  \phi + 2\pi R$, using the notation in Ref.~\onlinecite{di_francesco_conformal_1997}, we have the following mode expansion 
\begin{widetext}
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } -i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } ,
\end{aligned}
\end{equation}\end{widetext}
where $n,m$ are the momentum and winding modes quantum numbers.

In Ref.~\onlinecite{di_francesco_conformal_1997}, the quantization is performed on an equal time space. The boundary state we need here however lives on $x = 0$ -- a equal-space slice. We therefore compact the theory in the time direction with period $T$, and identify the holomorphic and anti-holomorphic coordinates as 
\begin{equation}
\label{eq:zzbar}
z = \exp( 2 \pi i \frac{t - x}{L}), \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L}).
\end{equation}
This corresponds to exchange the $x$ and $t$ in Ref.~\onlinecite{di_francesco_conformal_1997}.

### 2017-11-30 disc.tex
[paper] referee's suggestions done.

We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they are imposed on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group that can not be connected even by taking singular values of $\lambda$. It is then reasonable to find a universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of the completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}. We can first understand the values of several special points on this curve. 
\begin{itemize}
\item $\theta = 0$: This is where the boundary condition does not change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
\item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$. The chain is still disconnected after the change of the boundary conditions. We can thus view the problem as changing the boundary conditions for two independent chains in the left panel of Fig.~\ref{fig:echo}, one from D to N and the other from N to D. The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimensions are both $\Delta = \frac{1}{16}$. From this,
\begin{equation}
\begin{aligned}
  \quad \mathcal{L}(\tau) &\sim |\langle \phi_{{\rm D N}}(0) \phi_{{\rm ND}}(\tau)   \rangle |^2 
|\langle \phi_{{\rm ND}}(0)  \phi_{{\rm DN}}(\tau)   \rangle| ^2\\
& \sim \frac{1}{|\tau|^{8\Delta}} = \frac{1}{|\tau|^{\frac{1}{2}}},
\end{aligned}
\end{equation}
we can get the exponent to be $\frac{1}{2}$, which agrees with Fig.~\ref{fig:DDNN}. 
\item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$. The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
\end{itemize}
In general, the result gives the full spectrum of operator dimensions in the ${\rm DN} \rightarrow \lambda $ transition. In the bosonic CFT we consider, the primary fields are the vertex operators $\exp( \nu \phi )$. Depending on the convention, its dimension is a numerical constant times $\frac{\nu^2}{8\pi}$. So if $\nu$ depends linearly on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points above. In a rational CFT theory, the number of primary fields is finite. It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.

>>>>

We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they are imposed on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the dual field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group that can not be connected even by taking singular values of $\lambda$. It is then reasonable to find a universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of the completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

@@

For the more interesting case where the boundary conditions are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}. We can first understand the values of several special points on this curve. 
\begin{itemize}
\item $\theta = 0$: This is where the boundary condition does not change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
\item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$. The chain is still disconnected after the change of the boundary conditions. We can thus view the problem as changing the boundary conditions for two independent chains in the left panel of Fig.~\ref{fig:echo}, one from D to N and the other from N to D. The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimensions are both $\Delta = \frac{1}{16}$. From this,
\begin{equation}
\begin{aligned}
  \quad \mathcal{L}(\tau) &\sim |\langle \phi_{{\rm D N}}(0) \phi_{{\rm ND}}(\tau)   \rangle |^2 
|\langle \phi_{{\rm ND}}(0)  \phi_{{\rm DN}}(\tau)   \rangle| ^2\\
& \sim \frac{1}{|\tau|^{8\Delta}} = \frac{1}{|\tau|^{\frac{1}{2}}},
\end{aligned}
\end{equation}
we get the exponent to be $\frac{1}{2}$, which agrees with Fig.~\ref{fig:DDNN}. 
\item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$. The exponent $\frac{3}{8}$ agrees with Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice of the dimension of the bcc operator $\phi_{\rm DN}$ ($\Delta = \frac{1}{16}$) that transforms D to N.
\end{itemize}
In general, the result gives the full spectrum of operator dimensions in the ${\rm DN} \rightarrow \lambda $ transition. In the bosonic CFT we consider, the primary fields are the vertex operators $\exp( \nu \phi )$. Depending on the convention, its dimension is a numerical constant times $\frac{\nu^2}{8\pi}$. So if $\nu$ depends linearly on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points above. In a rational CFT theory, the number of primary fields is finite. It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.

### 2017-11-30 general_formulation.tex
[paper] referee's suggestions done.

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domains. We can therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}.
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission coefficient is $\pm \sin 2 \theta$.

@@

So far the derivation is only for the non-compact bosons, where the interface is determined by the ``gluing conditions''. For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$. Because the winding modes live on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$. App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$. For example, the $S_1(\theta)$ interface should satisfy
\begin{equation}
\lambda = \tan \theta = \frac{n_2 R_1}{n_1 R_2}
\end{equation}
for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on two sides. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by universal parameters of the CFTs on both sides.

The winding modes however do not contribute to the fidelity and echo exponent to the leader order, as shown in App.~\ref{app:compact_diff_boson}. So the derivations with the non-compact boson boundary state in Eq.~\eqref{eq:bd_state} holds true for the compact bosons.

>>>>

The physical significance of $\theta$ will be clear in the scattering process described below. We rewrite Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and use $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function of $t - x$ and hence represents a right going mode on the right half plane. This mode is one of the scattering modes that leave the interface. On the other hand, $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approach the interface from their respective domains. We can therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}.
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix},\
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}.
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission coefficient is $\sin^2 2 \theta$.

@@

So far the derivation is only for the non-compact bosons, where the interface is determined by the ``gluing conditions''. For the case of connecting compact bosons of different radii, we will need to generalize the relation in Eq.~\eqref{eq:rotation_a_basis} to the winding mode operator $a_0$. Because the winding modes live on a compactification lattice, not all $\theta$ can satisfy Eq.~\eqref{eq:rotation_a_basis} for $a_0$. App.~\ref{app:compact_diff_boson} reviews the derivation about how the winding modes constrain the choice of $\theta$. For example, the $S_1(\theta)$ interface should satisfy
\begin{equation}
\lambda = \tan \theta = \frac{n_2 R_1}{n_1 R_2}
\end{equation}
for coprime integer $n_1$ and $n_2$ and compactification radii $R_1$ and $R_2$ for the bosons on two sides. This also suggests that connecting two different CFTs will generate an interface whose transmission are determined by the universal parameters of the CFTs on both sides.

The winding modes however do not contribute to the fidelity and echo exponent to the leading order, as shown in App.~\ref{app:compact_diff_boson}. So the derivations with the non-compact boson boundary state in Eq.~\eqref{eq:bd_state} holds true for the compact bosons.

### 2017-11-30 gnd_dn_lambda.tex
[paper] referee's suggestions done.

The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as an orthonormal basis in the mode expansion, we thus have
\begin{equation}
\label{eq:H_in_gnd_dn_lambda}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right) ,
\end{equation}
where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators defined as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) ,\\
a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) .\\
\end{aligned}
\end{equation}

The Casimir energy is the vacuum energy brought up by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and using $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\
&= \frac{\pi}{2L} \Bigg( \sum_{n\ge 0 }  ( n + x ) + \sum_{n< 0 }  ( -n - x )  \\
&\quad \quad + \sum_{n \le 0}  (- n + x ) + \sum_{n > 0} ( n- x )  \Bigg) \\
&= \frac{\pi}{2L} \left( 2\sum_{n\ge 0 }  ( n + x ) + 2\sum_{n > 0} ( n- x )  \right).
\end{aligned}
\end{equation}
We use Hurwitz zeta function
\begin{equation}
\zeta_{\rm H}(s,x) = \sum_{n=0}^\infty\frac{1}{(n+x)^s}
\end{equation}
to regularize the sum, 
\begin{equation}
\begin{aligned}
E_c &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  -  (-x)^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, -x ) +  x \right] \\
&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
\end{aligned}
\end{equation}
where in the last line we use $L = 2\pi$ for the unfolded geometry.

>>>>

The normalized eigenfunctions in Eq.~\eqref{eq:normalized_f} serves as an orthonormal basis in the mode expansion, we thus have
\begin{equation}
\label{eq:H_in_gnd_dn_lambda}
H = \frac{1}{2} \sum_{n \in \mathbb{Z} } |k|  \left(a^{\dagger}_n a_n + \frac{1}{2} \right) ,
\end{equation}
where the momentum $k$ is defined in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, and the creation and annihilation operators are defined as usual
\begin{equation}
\begin{aligned}
a_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n + \frac{i }{\sqrt{|k|g} }\pi_n  \right) ,\\
a^{\dagger}_n = \frac{1}{\sqrt{2}} \left( \sqrt{ |k|g} \phi_n - \frac{i }{\sqrt{|k|g} }\pi_n  \right) .\\
\end{aligned}
\end{equation}

The Casimir energy is the vacuum energy brought up by the finite size of the setup. From Eq.~\eqref{eq:H_in_gnd_dn_lambda} and using $x\equiv \frac{\theta}{\pi}$ in Eq.~\eqref{eq:momentum_gnd_dn_lambda}, we have
\begin{equation}
\begin{aligned}
E_c &= \frac{1}{4} \sum_{n \in \mathbb{Z}} | k| = \frac{\pi}{2L} \left( \sum_{n \in \mathbb{Z}}  | n + x | + \sum_{n \in \mathbb{Z}}  | n - x |  \right) \\
&= \frac{\pi}{2L} \Bigg( \sum_{n\ge 0 }  ( n + x ) + \sum_{n< 0 }  ( -n - x )  \\
&\quad \quad + \sum_{n \le 0}  (- n + x ) + \sum_{n > 0} ( n- x )  \Bigg) \\
&= \frac{\pi}{2L} \left( 2\sum_{n\ge 0 }  ( n + x ) + 2\sum_{n > 0} ( n- x )  \right).
\end{aligned}
\end{equation}
We use the Hurwitz zeta function
\begin{equation}
\zeta_{\rm H}(s,x) = \sum_{n=0}^\infty\frac{1}{(n+x)^s}
\end{equation}
to regularize the sum, 
\begin{equation}
\begin{aligned}
E_c &= \frac{\pi}{L} \Big[\sum_{n \ge 0 } ( n + x )^{-s} + \sum_{n \ge 0 }  ( n - x)^{-s}  -  (-x)^{-s} \Big]\Big|_{s = -1} \\
&= \frac{\pi}{L} \left[ \zeta_{\rm H}( -1, x ) + \zeta_{\rm H}( -1, -x ) +  x \right] \\
&= \frac{1}{2} \left( - x^2 + x - \frac{1}{6}\right),
\end{aligned}
\end{equation}
where in the last line we use $L = 2\pi$ for the unfolded geometry.
